Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-03-24 manuscript/manuscript.Rmd
updates figures

\textsf{\normalsize{\textbf{Andrew T. Tredennick\textsuperscript{1}\footnote{Corresponding author: atredenn@gmail.com}, Mevin B. Hooten\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}}}

@@

How might we improve on this state of affairs? First, forecasts could be improved by matching the spatial scale of predictor variables with the spatial scale of observations. One of the major limitations of the models we fit here is that the climate data are collected at a larger scale than the individual-level observations of plant size. Climate covariates only vary by year, with no spatial variability within years. Thus, even if we fit models to individual-level data, we are missing the key interaction point between weather and individual plants [@Clark2011b] because all observations share the same climate covariates. Demographic studies should be designed with at least plot-level measurements of climate related variables (e.g., soil moisture). Second, accurately detecting climate signals will take even longer time series. Recent theoretical work on detecting climate signals in noisy data suggests that even advanced approaches to parameter fitting require 20-25 year time series [@Tellerinpress]. Third, ecologists need a stronger commitment to reporting uncertainty. Although most modeling studies explicitly consider model uncertainty, parameter uncertainty is often ignored. In some cases this is because the most convenient statistical methods make it difficult to propogate parameter uncertainty. Yet even Bayesian approaches that allow integration of model fitting and forecasting [@Hobbs2015] are not simple when using modeling approaches like integral projection models that separate the model fitting and simulation stages [@Rees2009]. However, as we have done here, it is still possible to include parameter uncertainty by drawing parameter values from MCMC iterations, taking care to draw all parameters from the same chain and iteration to account for their correlations. Only by being honest about our forecasts can we begin to produce better ones, and forecasts reported without parameter error are disingenuous.  Ignoring parameter error may be justifiable when the goal is investigating basic processes, but it is indefensible when forecasting is the goal.

@@

```{r figure_2,dependson="plot-options", fig.cap="Work flow of the data aggregation, model fitting, and population simulating.", fig.height=6, eval=F}
library(png)
library(grid)
img <- readPNG("components/figure/micromeso_flowchart.png")
grid.raster(img)
```

@@

\setcounter{page}{24}

>>>>

\textsf{\normalsize{\textbf{Andrew T. Tredennick\textsuperscript{1}\footnote{Corresponding author: E-mail: atredenn@gmail.com}, Mevin B. Hooten\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}}}

@@

How might we improve on this state of affairs? First, forecasts could be improved by matching the spatial scale of predictor variables with the spatial scale of observations. One of the major limitations of the models we fit here is that the climate data are collected at a larger scale than the individual-level observations of plant size. Climate covariates only vary by year, with no spatial variability within years. Thus, even if we fit models to individual-level data, we are missing the key interaction point between weather and individual plants [@Clark2011b] because all observations share the same climate covariates. Demographic studies should be designed with at least plot-level measurements of climate related variables (e.g., soil moisture). Second, accurately detecting climate signals will take even longer time series. Recent theoretical work on detecting climate signals in noisy data suggests that even advanced approaches to parameter fitting require 20-25 year time series [@Teller2016]. Third, ecologists need a stronger commitment to reporting uncertainty. Although most modeling studies explicitly consider model uncertainty, parameter uncertainty is often ignored. In some cases this is because the most convenient statistical methods make it difficult to propogate parameter uncertainty. Yet even Bayesian approaches that allow integration of model fitting and forecasting [@Hobbs2015] are not simple when using modeling approaches like integral projection models that separate the model fitting and simulation stages [@Rees2009]. However, as we have done here, it is still possible to include parameter uncertainty by drawing parameter values from MCMC iterations, taking care to draw all parameters from the same chain and iteration to account for their correlations. Only by being honest about our forecasts can we begin to produce better ones, and forecasts reported without parameter error are disingenuous.  Ignoring parameter error may be justifiable when the goal is investigating basic processes, but it is indefensible when forecasting is the goal.

@@

\newpage{}

```{r figure_2,dependson="plot-options", fig.cap="Work flow of the data aggregation, model fitting, and population simulating.", fig.height=4, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/micromeso_flowchart.png")
grid.raster(img)
```

\newpage{}

@@

\singlespace{}
